---
title: "p8105_hw3_jx2371"
author: "Jingyu Xu"
date: "2018/10/13"
output: github_document
---

---
title: "P8105_hw3_jx2371"
author: "Jingyu Xu"
date: "2018/10/13"
output: github_document
---
Firstly，I set a globle option which hides the message and warning information.
```{r setup}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
```

#Problem 1
##data cleaning
Firstly，I did some data cleaning in this code chunck
format the data to use appropriate variable names； 
focus on the “Overall Health” topic； 
include only responses from “Excellent” to “Poor”  
organize responses as a factor taking levels ordered from “Excellent” to “Poor”  

```{r}
library(p8105.datasets)
library(tidyverse)
brfss = brfss_smart2010 %>%
  janitor::clean_names() %>%
  rename(state=locationabbr,location=locationdesc)%>%
  filter(topic == "Overall Health") %>% 
  filter(response == "Excellent"|response == "Very good"|response == "Good"|response == "Fair"|response == "Poor")%>%
  mutate(response=as.factor(response))
levels(brfss$response)=c("Excellent","Very good","Fair","Good","Poor")
```


