---
title: "p8105_hw3_jx2371"
author: "Jingyu Xu"
date: "2018/10/13"
output: github_document
---
Firstly，I set a globle option which hides the message and warning information.
```{r setup}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
```

#Problem 1
##data cleaning
Firstly，I did some data cleaning in this code chunck
format the data to use appropriate variable names； 
focus on the “Overall Health” topic； 
include only responses from “Excellent” to “Poor”  
organize responses as a factor taking levels ordered from “Excellent” to “Poor”  

```{r}
library(p8105.datasets)
library(tidyverse)
brfss = brfss_smart2010 %>%
  janitor::clean_names() %>%
  rename(state=locationabbr,location=locationdesc)%>%
  filter(topic == "Overall Health") %>% 
  filter(response == "Excellent"|response == "Very good"|response == "Good"|response == "Fair"|response == "Poor")%>%
  mutate(response=as.factor(response))
levels(brfss$response)=c("Excellent","Very good","Fair","Good","Poor")
```

##answering questions
1.selecting the states that were observed at 7 locations in 2002
```{r}
brfss%>%
  filter(year==2002)%>%
  group_by(state,location) %>%
  summarize(n = n())%>%
  count(state)%>%
  filter(nn==7)
```
we can see from the result of the code chunk that CT,FL and NC had 7 locations observed in 2002.

2.draw a spaghetti plot showing the number of locations in each state from 2002 to 2010
```{r fig.height=8}
brfss%>%
  group_by(state, year,location)%>%
  summarize(n=n())%>%
  group_by(state, year)%>%
  summarize(number=n())%>%
  ggplot(aes(x = year, y = number, color = state)) + 
  geom_line(size=0.3) +
  theme(legend.position = "bottom")
```
We observe from the soaghetti plot that the trend of locations in most of the states is somehow stable, with little fluctuation. On the other hand, FL is unique in these observations that it changes dramatically by the year and reaches 40 in 2010, which is the most among all the states.  

3.we can see from the dataset that the column data_value refer to the proportion(%). To make it clear, I create a new column named "proportion" in percentage and select the data of 2002，2006 and 2010. Then, I caculate the mean and variance of the excellent data across locations in United states
```{r}
excellent_data=filter(brfss,year=="2002" | year=="2006" |year=="2010",response=="Excellent",state=="NY")%>%
  select(year,state,location,response,data_value)%>%
  mutate(data_value=data_value/100)%>%
  rename(proportion=data_value)

mean_2002=mean((subset(excellent_data, year=="2002"))$proportion,na.rm = TRUE)
standard_var_2002=sqrt(var((subset(excellent_data, year=="2002"))$proportion,na.rm = TRUE))
mean_2006=mean((subset(excellent_data, year=="2006"))$proportion,na.rm = TRUE)
standard_var_2006=sqrt(var((subset(excellent_data, year=="2006"))$proportion,na.rm = TRUE))
mean_2010=mean((subset(excellent_data, year=="2010"))$proportion,na.rm = TRUE)
standard_var_2010=sqrt(var((subset(excellent_data, year=="2010"))$proportion,na.rm = TRUE))
```
now a table is create:
```{r}
tibble(year=c("2002", "2006", "2010"), standard_variance=c(standard_var_2002,standard_var_2006,standard_var_2010),
                      mean=c(mean_2002, mean_2006, mean_2010))%>%
knitr::kable()
```



4.For each year and state, compute the average proportion in each response category (taking the average across locations in a state). Make a five-panel plot that shows, for each response category separately, the distribution of these state-level averages over time.
```{r fig.width=15, fig.height=10}
brfss%>%
  select(year,state,location, response, data_value)%>%
  group_by(year,state,response)%>%
  summarise(average_proportion=mean(data_value))%>%
  ggplot(aes(x = factor(year), y = average_proportion, fill=factor(year))) + 
  geom_boxplot()+
  labs(
    title = "the average proportion in each response category",
    x = "the year observed",
    y = "average proportion",
    caption = "Data from the brfss package"
  )+
  viridis::scale_color_viridis(
    name = "year", 
    discrete = TRUE
  ) + 
  facet_grid(.~response)+
  theme(legend.position = "bottom")+
  theme(axis.text.x = element_text(face="bold",size=10, angle = 90))
```
We can observe from the boxplots that the average proportion ordered from highest to the lowest from an overall average trend aspect is:poor response, fair response, excellent response, very good response and good response. And there are some outliers in all of the response section.

#Problem2
Firstly, import the instacat data
```{r}
instacart=instacart
```
##brief description of the dataset
The size of dataset is （`r dim(instacart)`). The variables includes "`r names(instacart)`". The type and menaing of each variables are displayed in the chunk below:
```{r}
str(instacart)
```

##answers to some questions
1.number of aisles and select the aisles the most items ordered from.
```{r}
#caculate the number of aisles
instacart%>%
  distinct(aisle_id)%>%
  nrow()

#select the aisles the most items ordered from
number_item=instacart%>%
  group_by(aisle)%>%
  summarize(order_total=n())%>%
  arrange(-order_total)

number_item
```

comment:
From the result of the code chunck, we can see the total number of aisles is 134 and the aisle that most items orderd from is fresh vegetables.


2. Draw a plot that shows the number of items in each aisle.
```{r fig.height=20}
number_item%>%
ggplot(aes(x = order_total, y=aisle)) + 
  geom_bar(stat="identity")+
  labs(
    title = "the number of items in each aisle",
    x = "the total number of item",
    y = "aisle name",
    caption = "Data from the instacart package"
  )+
  theme(axis.text.x = element_text(face="bold",size=10, angle = 90))
```


3.make a table showing the most popular item in each of the aisles"baking ingredients", "dog food care", "packaged vegetables fruits"
```{r}
filter(instacart, aisle=="baking ingredients"|aisle=="dog food care"|aisle=="packaged vegetables fruits")%>%
  group_by(aisle,product_name)%>%
  summarize(n=n())%>%
  group_by(aisle)%>%
  filter(n==max(n))%>%
    knitr::kable()
```

Comment:Now, we have got the table of the most populer items in the aisles selected.Light brown sugar is the most popular item in the aisle"baking ingredients", and Snack Sticks Chicken & Rice Recipe Dog Treats is the most popular item in the aisle"dog food care". As for the most popular item in packaged vegetables fruits, it is Organic Baby Spinach.
